Turbulence in compact to giant HII regions

### 2022-02-13 strucfunc_paper.tex
Minor change
Add figure for the model structure function

@@

For separations that are comparable to the diameter \(D\) of the \hii{} region,
then the supposition of homogeneity must break down.
For instance, if the amplitude of the velocity fluctuations is higher
in the core of the region than in the outskirts,
then the autocorrelation function will be U-shaped
since all separations with \(r > D/2\) must be between two points in the outskirts,
which will tend to be relatively well correlated simply because both velocities
will be close to the mean.
This yields a corresponding downturn in the structure function at the largest scales.

>>>>

\begin{figure*}
 \centering
 \includegraphics[width=\linewidth]{Figures/model-strucfunc-annotated}\par
 \caption{
   A model structure function for homogeneous fluctuations.
   (a)~Idealized structure function (blue line) and effects
   of observational limitations at small and large scales.
   (b)~Examples of inhomogeneous effects at large scales,
   which are not included in the model structure function.
 }
 \label{fig:model-strucfunc}
\end{figure*}

@@

For separations that are comparable to the diameter \(D\) of the \hii{} region,
then the supposition of homogeneity may break down.
For instance, if the amplitude of the velocity fluctuations is higher
in the core of the region than in the outskirts,
then the autocorrelation function will be U-shaped
since all separations with \(r > D/2\) must be between two points in the outskirts,
which will tend to be relatively well correlated simply because both velocities
will be close to the mean.
This yields a corresponding downturn in the structure function at the largest scales.
